Relative parabolic factorizations of Chevalley groups

### 2015-09-18 dennis-vaserstein.tex
Minor fixes

By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1,2} = 0$.
Consequently, for every $g\in C$ one has
\begin{multline*}
 \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
\end{multline*}
Direct calculation using \cref{lemma:Chevalley-Matsumoto} shows that $(yg)^{x_{2,1}(\xi)} = u h$ for $\xi \in R$, $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$ hence
\begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
 \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1} \end{multline*}
 as claimed.
\end{proof}

>>>>

By the very definition of $C$, for every $g \in C$ one can choose $y \in \U(\Sigma_1 \cap \Delta_\ell, I)$ such that $(y \cdot g)_{1,2} = 0$.
Consequently, for every $g\in C$ one has
\begin{multline*}
 \EP_\ell(R, I) \cdot \U(\Sigma_1^- \cap \Sigma_\ell^-, I) \cdot g \subseteq \EP_\ell(R, I) y^{-1} \cdot \U(\Sigma_\ell^-\cap \Sigma_1^-, I)^{y^{-1}} \cdot y g \subseteq \\
  \subseteq \EP_\ell(R, I) \cdot \U(\Sigma_\ell^-, I) \cdot y g
\end{multline*}
Notice that the matrix entry $(yg)_{1,1}$ is invertible.
From the choice of $y$ it follows that for every $\xi\in R$ the element $g_1:=(yg)^{x_{2,1}(\xi)}$
satisfies the assumptions of \cref{lemma:Chevalley-Matsumoto} and therefore can be rewritten as $g_1 = uh$ for some $u \in \U(\Sigma_1^-, I)$, $h \in \EP_1(R, I)$.
Consequently, one has
\begin{multline*} {A_{\ell,1}}^{X_{-\alpha_1}(R)} = A'^{X_{2,1}(R)} \subseteq \EP_\ell(R, I)^{X_{2,1}(R)} \cdot \U(\Sigma_\ell^-, I)^{X_{2,1}(R)} \cdot \U(\Sigma_1^-, I) \cdot \EP_1(R, I) \subseteq \\
 \subseteq \EP_\ell(R, I) \cdot \U(\Phi^-, I) \cdot \EP_1(R, I) \subseteq A_{\ell,1} \end{multline*}
 as claimed.
\end{proof}

### 2015-09-18 stability-conditions.tex
Minor fixes

\subsection{Action of unipotent radicals}\label{sec:ur-action}
Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$, i.e. $v_+=(v_1,\ldots, v_\ell)^t$, $v_-=(v_{-\ell},\ldots, v_{-1})^t$.
\begin{lemma}\label{lemma:asrUnip}
Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \G(\Phi, R, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
\begin{lemlist}
\item \label{item:asrUnipC} $\Phi=\rC_\ell$ and $\sr(I) \leqslant \ell$;
\item \label{item:asrUnipD} $\Phi=\rD_\ell$ and $\asr(I)\leqslant \ell -1$.
\end{lemlist}
\end{lemma}
\begin{proof} 
\textsc{Case $\Phi=\rC_\ell$.}
Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$. 
Set $d =\mathrm{diag}(v_{-\ell},\ldots,v_{-1}).$
Notice that the column $$v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$$ is also $I$-unimodular.
By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$
such that the upper half $v''_+$ of the vector $v''= g(b) \cdot v'$, where 
$g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$, is $I$-unimodular.
It is clear that $v''_+ = v'_+ + pb v'_- = v_+ + pbd v_-$. 
Consider the matrix $a \in M(\ell, I)$ defined by 
\begin{align*}
 & a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ j\neq i,\\
 & a_{ii} = b_{ii} v_{-i} - \sum\limits_{j=1, j\neq i}^\ell b_{ji} v_{-j}.
\end{align*}
It is clear that the matrix $pa$ is persymmetric and that $g(a) \in \U(\Sigma_\ell, I)$. 
On the other hand, direct calculation shows that $(g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbdv_- = v''_+ \in \Ums(\ell, I)$.
%$$(av_-)_k = \sum\limits_{i=1,\ i\neq k}^\ell \left( b_{ki} v_{-i} + b_{ik} v_{-k} \right)v_{-i}  +
%\left(b_{kk}v_{-k} - \sum\limits_{i=1,\ i\neq k}^\ell b_{ik} v_{-i}\right)v_{-k} = \sum\limits_{i=1}^\ell b_{ki} v_{-i}^2 = (bdv_-)_k$$

>>>>

\subsection{Action of unipotent radicals}\label{sec:ur-action}
Let $v\in V=R^{2\ell}$ be a vector of the natural representation of $\G(\rD_\ell, R)$.
Denote by $v_+$ and $v_-$ the upper and the lower halves of $v$, i.e. $v_+=(v_1,\ldots, v_\ell)^t$, $v_-=(v_{-\ell},\ldots, v_{-1})^t$.
\begin{lemma}\label{lemma:asrUnip}
Then for any $I$-unimodular column $v=(v_+, v_-)^t\in\Ums(2\ell, I)$ there exists $g\in\U(\Sigma^+_\ell, I) \leq \G(\Phi, R, I)$ such that $(g \cdot v)_+ \in \Ums(\ell, I)$ under the following assumptions on $\Phi$ and $I$.
\begin{lemlist}
\item \label{item:asrUnipC} $\Phi=\rC_\ell$ and $\sr(I) \leqslant \ell$;
\item \label{item:asrUnipD} $\Phi=\rD_\ell$ and $\asr(I)\leqslant \ell -1$.
\end{lemlist}
\end{lemma}
\begin{proof} 
\textsc{Case $\Phi=\rC_\ell$.}
Denote by $p$ the matrix of size $\ell$ such that its only nonzero entries equal $1$ and are located on the skew-diagonal, i.\,e. $p_{ij}=(\delta_{i, \ell-j+1})$. 
Set $d =\mathrm{diag}(v_{-\ell},\ldots,v_{-1}).$
Notice that the column $$v'=(v_1,\ldots,v_\ell, v_{-\ell}^2,\ldots,v_{-1}^2)^t$$ is also $I$-unimodular.
By the definition of the relative stable rank we can find a matrix $b\in \M(\ell,I)$
such that the upper half $v''_+$ of the vector $v''= g(b) \cdot v'$, where 
$g(b)=\left(\begin{smallmatrix} e_\ell & p \cdot b \\ 0 & e_{\ell} \end{smallmatrix}\right)$, is $I$-unimodular.
It is clear that $v''_+ = v'_+ + pb v'_- = v_+ + pbd v_-$. 
Consider the matrix $a \in M(\ell, I)$ defined by 
\begin{align*}
 & a_{ij} = b_{ij} v_{-j} + b_{ji} v_{-i},\ j\neq i,\\
 & a_{ii} = b_{ii} v_{-i} - \sum\limits_{\mathclap{\substack{j=1 \\ j\neq i}}}^\ell b_{ji} v_{-j}.
\end{align*}
It is clear that the matrix $pa$ is persymmetric and that $g(a) \in \U(\Sigma_\ell, I)$. 
On the other hand, direct calculation shows that $(g(a)\cdot v)_+=v_+ + pav_- = v_+ + pbdv_- = v''_+ \in \Ums(\ell, I)$.
%$$(av_-)_k = \sum\limits_{i=1,\ i\neq k}^\ell \left( b_{ki} v_{-i} + b_{ik} v_{-k} \right)v_{-i}  +
%\left(b_{kk}v_{-k} - \sum\limits_{i=1,\ i\neq k}^\ell b_{ik} v_{-i}\right)v_{-k} = \sum\limits_{i=1}^\ell b_{ki} v_{-i}^2 = (bdv_-)_k$$
